Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
it's certain THAT something is true.

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and has seen multiple extensions over the years.  Although
it's pretty certain extensions to these languages that are published are
correct, requiring these extensions to be added to a verified compiler would
help ensure that the language updates will not invalidate pre-existing security
properties of the language, because adding the extension would require adding
code to cover the additional cases in the proofs.

>>>>

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and has seen multiple extensions over the years.  Although
it's pretty certain that extensions to these languages that are published are
correct, requiring these extensions to be added to a verified compiler would
help ensure that the language updates will not invalidate pre-existing security
properties of the language, because adding the extension would require adding
code to cover the additional cases in the proofs.
